---
title: "Moral ID and COVID"
subtitle: "Alternative Analysis"
author: "Cillian McHugh"
date: "21st May 2021"
bibliography      : "../../Research_general/resources/bib/My Library.bib"
csl: "../../Research_general/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{=html}
<style type="text/css">
  .table-container {
  width: 100%;
  overflow-x: scroll;
}
</style>
```
# Introduction

[Introduction is here](https://docs.google.com/document/d/1mDV7E6DE7lUiBEDMDcoaAhFGffB4TgVT1DAzisn6kWE/edit?usp=sharing)

```{r setup, include = FALSE}
rm(list=ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
library(desnum)
library(papaja)
library(purrr)
library(interactions)
library(kableExtra)
library("papaja")
library(lme4)
library(car)
library(ggplot2)
library(nlme)
library(reshape)

r_refs("r-references.bib")
```

```{r analysis-preferences, include=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)

```

```{r load_data}
#setwd("../../COVID_19/moral_paper_draft")
#source("set_up_data.R")
load("../many_labs/COVID_manylabs_data.RData")

World_full_c_unscaled <- World_full_c

World_full_scaled <- 
  World_full_c %>% mutate(
      policy_support_tot = scale(policy_support_tot)
    , physical_hygiene_tot = scale(physical_hygiene_tot)
    , physical_contact_tot = scale(physical_contact_tot)
    , risk_perception_tot = scale(risk_perception_tot)
    , narcissism_admiration_tot = scale(narcissism_admiration_tot)
    , narcissism_rivalry_tot = scale(narcissism_rivalry_tot)
    , collective_narcissism_tot = scale(collective_narcissism_tot)
    , conspiracy_tot = scale(conspiracy_tot)
    , national_ID_tot = scale(national_ID_tot)
    , moral_circle = scale(moral_circle)
    , moral_identity_internal = scale(moral_identity_internal)
    , moral_identity_symbolic = scale(moral_identity_symbolic)
  )

world_ful_c <- World_full_scaled

df <- World_full_c

```

# Method

## Participants

A total of sample of *N* = `r length(df$sex)` participants (`r sum(df$sex==1, na.rm=T)`, female, `r sum(df$sex==2, na.rm=T)` male, `r sum(df$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(df$age,na.rm=T),digits=2)`, min = 18, max = 100, *SD* = `r round(sd(df$age,na.rm=T),digits=2)`), were recruited from `r length(levels(df$country))` countries.


```{r}
df <- World_full_scaled
df <- df[which(df$country=="USA"|df$country=="NZL"),]
table(df$country)
df$country <- droplevels(df$country)

```


```{r include = F}

df$Country <- car::recode(df$country, "'USA'='0'; 'NZL'='1'")
df$Country <- as.numeric(as.character((df$Country)))

nzl <- df[which(df$country=="NZL"),]
usa <- df[which(df$country=="USA"),]

```

I isolated just the participants in USA and NZL, leaving a total of *N* = `r length(df$sex)` participants (`r sum(df$sex==1, na.rm=T)`, female, `r sum(df$sex==2, na.rm=T)` male, `r sum(df$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(df$age,na.rm=T),digits=2)`, min = 18, max = 100, *SD* = `r round(sd(df$age,na.rm=T),digits=2)`). The USA sample consisted of *n* = `r length(usa$sex)` participants (`r sum(usa$sex==1, na.rm=T)`, female, `r sum(usa$sex==2, na.rm=T)` male, `r sum(usa$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(usa$age,na.rm=T),digits=2)`; and the New Zealand sample consisted of *n* = `r length(nzl$sex)` participants (`r sum(nzl$sex==1, na.rm=T)`, female, `r sum(nzl$sex==2, na.rm=T)` male, `r sum(nzl$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(nzl$age,na.rm=T),digits=2)`.


# Results

# Policy Support
```{r}

df <- df[which(is.na(df$policy_support_tot)==FALSE),]
#df <- df[which(is.na(df$physical_hygiene_tot)==FALSE),]
#df <- df[which(is.na(df$physical_contact_tot)==FALSE),]

df <- df[which(is.na(df$moral_identity_internal)==FALSE),]
df <- df[which(is.na(df$moral_identity_symbolic)==FALSE),]
df <- df[which(is.na(df$moral_circle)==FALSE),]
df <- df[which(is.na(df$political_ideology)==FALSE),]

```

## Without Country

```{r include = F}

fit1 <- lm(
  policy_support_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = df)
summary(fit1)

apa_lm <- apa_print(fit1)

```

First I ran a regression for all variables across the full dataset (without accounting for Country). This model was significant `r apa_lm$full_result$modelfit`.

```{r regression, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Policy Support (without Country)"
)

```


```{r}

fit2 <- lm(policy_support_tot ~ Country * (risk_perception_tot
                                          + narcissism_admiration_tot
                                          + narcissism_rivalry_tot
                                          + collective_narcissism_tot
                                          + conspiracy_tot
                                          + national_ID_tot
                                          + # add predictors
                                          + moral_circle
                                          + moral_identity_internal
                                          + moral_identity_symbolic
                                          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)), data = df)
summary(fit2)

apa_lm <- apa_print(fit2)


a <- anova(fit1,fit2)


a$Df[2]
a$Res.Df[2]
a$F
p <- a$`Pr(>F)`[2]


apa_lm$table$p.value[29]


```

## With Country

Next I added Country as an interaction term. Again the model was significant `r apa_lm$full_result$modelfit`. And the model performed significantly better than the previous model *F*(`r round(a$Df[2], digits=2)`, `r round(a$Res.Df[2], digits=2)`) = `r round(a$F[2], digits =2)`, *p* `r paste(p_report(p))`. Most interestingly, the three way interaction between Country, Political Ideology, and Moral Identity Internal is there:

```{r, include=FALSE}

c <- apa_lm$table[29,]

```


```{r interaction, include=TRUE}

apa_table(
  c
  , caption = "3 way interaction"
)

```

```{r regression2, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Policy Support (with Country)"
)

```


```{r}

interaction_fun <- function(x){
  case_when(x > mean(x,na.rm=T)+sd(x,na.rm=T) ~ "1conservative/right",
            x < mean(x,na.rm=T)+sd(x,na.rm=T) & x > mean(x,na.rm=T)-sd(x,na.rm=T) ~ "2moderate/centre",
            x < mean(x,na.rm=T)-sd(x,na.rm=T) ~ "3liberal/left")
}


df <-
  df %>%
  dplyr::group_by(country) %>%
  dplyr::mutate(political_ideology_3groups = interaction_fun(political_ideology)
                , national_pi_mean = mean(political_ideology)
                , national_pi_sd = sd(political_ideology))

```

## Plot

Figure \@ref(fig:policyMIsNZLUSA1) shows the relationship between Political Ideology and Internal Moral Identity in predicting Policy Support for the New Zealand sample and the USA sample separately.

```{r policyMIsNZLUSA1, fig.cap="USA: Interaction between Political Ideology and Internal Moral Identity in predicting Policy Support", include=TRUE, message=FALSE, fig.height=3}
df1 <- df[which(df$country=="USA"|df$country=="NZL"),]
g <- ggplot(df1, aes(moral_identity_internal, policy_support_tot, linetype =political_ideology_3groups))+
  geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
  #ylim(0,12) +
  geom_smooth(method=lm, size = .5, color="black") +
  labs(y = "Policy Support",
       x = "Internal Moral Identity",
       linetype = "Political Ideology"
       )+
  theme_apa()+
  scale_linetype_manual(values = c("longdash", "solid", "dotted"),
                    labels=c("Conservative",
                           "Moderate",
                           "Liberal"))+
  facet_wrap(df1$country)+
  theme_bw()+
  theme(plot.title=element_text(#family="Times",
                                size=12
                                )
        , legend.text=element_text(#family="Times",
                                 size=8
                                 )
        , legend.title=element_text(#family="Times",
                                    size=10
                                    )
        , axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 )
        , axis.ticks.x = element_blank()
        , axis.title=element_text(#family="Times",
                                  size=12
                                  )
        , strip.text=element_text(#family = "Times",
                                  size = 12
                                  )
        , strip.background = element_rect(fill = NA, size = 1,
                                           colour = "white"
                                          )
        , panel.border = element_blank()
        , axis.line.x = element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , axis.line.y = # element_blank()
          element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , legend.position="right"
        , panel.spacing = unit(2, "lines")
        )

suppressWarnings(print(g))
  
```

## USA Regression

```{r}
fit1 <- lm(
  policy_support_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = usa)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r usaregression1, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Policy Support in USA"
)

```


## New Zealand Regression

```{r}
fit1 <- lm(
  policy_support_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = nzl)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r nzlregression1, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Policy Support in New Zealand"
)

```

# Physical Contact
```{r}

#df <- df[which(is.na(df$policy_support_tot)==FALSE),]
#df <- df[which(is.na(df$physical_hygiene_tot)==FALSE),]
df <- df[which(is.na(df$physical_contact_tot)==FALSE),]

df <- df[which(is.na(df$moral_identity_internal)==FALSE),]
df <- df[which(is.na(df$moral_identity_symbolic)==FALSE),]
df <- df[which(is.na(df$moral_circle)==FALSE),]
df <- df[which(is.na(df$political_ideology)==FALSE),]

```

## Without Country

```{r include = F}

fit1 <- lm(
  physical_contact_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = df)
summary(fit1)

apa_lm <- apa_print(fit1)

```

First I ran a regression for all variables across the full dataset (without accounting for Country). This model was significant `r apa_lm$full_result$modelfit`.

```{r regression3, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Physical Contact (without Country)"
)

```


```{r}

fit2 <- lm(physical_contact_tot ~ Country * (risk_perception_tot
                                          + narcissism_admiration_tot
                                          + narcissism_rivalry_tot
                                          + collective_narcissism_tot
                                          + conspiracy_tot
                                          + national_ID_tot
                                          + # add predictors
                                          + moral_circle
                                          + moral_identity_internal
                                          + moral_identity_symbolic
                                          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)), data = df)
summary(fit2)

apa_lm <- apa_print(fit2)


a <- anova(fit1,fit2)


a$Df[2]
a$Res.Df[2]
a$F
p <- a$`Pr(>F)`[2]


apa_lm$table$p.value[29]


```

## With Country

Next I added Country as an interaction term. Again the model was significant `r apa_lm$full_result$modelfit`. And the model performed significantly better than the previous model *F*(`r round(a$Df[2], digits=2)`, `r round(a$Res.Df[2], digits=2)`) = `r round(a$F[2], digits =2)`, *p* `r paste(p_report(p))`. Again a three way interaction was observed.


```{r, include=FALSE}

c <- apa_lm$table[29,]

```


```{r interaction2, include=TRUE}

apa_table(
  c
  , caption = "3 way interaction"
)

```

```{r regression4, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Physical Contact (with Country)"
)

```


```{r}

interaction_fun <- function(x){
  case_when(x > mean(x,na.rm=T)+sd(x,na.rm=T) ~ "1conservative/right",
            x < mean(x,na.rm=T)+sd(x,na.rm=T) & x > mean(x,na.rm=T)-sd(x,na.rm=T) ~ "2moderate/centre",
            x < mean(x,na.rm=T)-sd(x,na.rm=T) ~ "3liberal/left")
}


df <-
  df %>%
  dplyr::group_by(country) %>%
  dplyr::mutate(political_ideology_3groups = interaction_fun(political_ideology)
                , national_pi_mean = mean(political_ideology)
                , national_pi_sd = sd(political_ideology))

```

## Plot

Figure \@ref(fig:contactMIsNZLUSA1) shows the relationship between Political Ideology and Internal Moral Identity in predicting Physical Hygiene for the New Zealand sample and the USA sample separately.

```{r contactMIsNZLUSA1, fig.cap="USA: Interaction between Political Ideology and Internal Moral Identity in predicting Physical Hygiene", include=TRUE, message=FALSE, fig.height=3}
df1 <- df[which(df$country=="USA"|df$country=="NZL"),]
g <- ggplot(df1, aes(moral_identity_internal, physical_contact_tot, linetype =political_ideology_3groups))+
  geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
  #ylim(0,12) +
  geom_smooth(method=lm, size = .5, color="black") +
  labs(y = "Physical Contact",
       x = "Internal Moral Identity",
       linetype = "Political Ideology"
       )+
  theme_apa()+
  scale_linetype_manual(values = c("longdash", "solid", "dotted"),
                    labels=c("Conservative",
                           "Moderate",
                           "Liberal"))+
  facet_wrap(df1$country)+
  theme_bw()+
  theme(plot.title=element_text(#family="Times",
                                size=12
                                )
        , legend.text=element_text(#family="Times",
                                 size=8
                                 )
        , legend.title=element_text(#family="Times",
                                    size=10
                                    )
        , axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 )
        , axis.ticks.x = element_blank()
        , axis.title=element_text(#family="Times",
                                  size=12
                                  )
        , strip.text=element_text(#family = "Times",
                                  size = 12
                                  )
        , strip.background = element_rect(fill = NA, size = 1,
                                           colour = "white"
                                          )
        , panel.border = element_blank()
        , axis.line.x = element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , axis.line.y = # element_blank()
          element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , legend.position="right"
        , panel.spacing = unit(2, "lines")
        )

suppressWarnings(print(g))
  
```

## USA Regression

```{r}
fit1 <- lm(
  physical_hygiene_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = usa)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r usaregression2, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Adherence to Physical Contact measures in USA"
)

```


## New Zealand Regression

```{r}
fit1 <- lm(
  physical_hygiene_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = nzl)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r nzlregression2, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Adherence to Physical Contact measures in New Zealand"
)

```





# Physical Hygiene
```{r}

#df <- df[which(is.na(df$policy_support_tot)==FALSE),]
df <- df[which(is.na(df$physical_hygiene_tot)==FALSE),]
#df <- df[which(is.na(df$physical_contact_tot)==FALSE),]

df <- df[which(is.na(df$moral_identity_internal)==FALSE),]
df <- df[which(is.na(df$moral_identity_symbolic)==FALSE),]
df <- df[which(is.na(df$moral_circle)==FALSE),]
df <- df[which(is.na(df$political_ideology)==FALSE),]

```

## Without Country

```{r include = F}

fit1 <- lm(
  physical_hygiene_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = df)
summary(fit1)

apa_lm <- apa_print(fit1)

```

First I ran a regression for all variables across the full dataset (without accounting for Country). This model was significant `r apa_lm$full_result$modelfit`.

```{r regression5, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Physical Hygiene (without Country)"
)

```


```{r}

fit2 <- lm(physical_hygiene_tot ~ Country * (risk_perception_tot
                                          + narcissism_admiration_tot
                                          + narcissism_rivalry_tot
                                          + collective_narcissism_tot
                                          + conspiracy_tot
                                          + national_ID_tot
                                          + # add predictors
                                          + moral_circle
                                          + moral_identity_internal
                                          + moral_identity_symbolic
                                          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)), data = df)
summary(fit2)

apa_lm <- apa_print(fit2)


a <- anova(fit1,fit2)


a$Df[2]
a$Res.Df[2]
a$F
p <- a$`Pr(>F)`[2]


apa_lm$table$p.value[29]


```

## With Country

Next I added Country as an interaction term. Again the model was significant `r apa_lm$full_result$modelfit`. And the model performed significantly better than the previous model *F*(`r round(a$Df[2], digits=2)`, `r round(a$Res.Df[2], digits=2)`) = `r round(a$F[2], digits =2)`, *p* `r paste(p_report(p))`. No three way interaction this time.

```{r regression6, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Physical Hygiene (with Country)"
)

```


```{r}

interaction_fun <- function(x){
  case_when(x > mean(x,na.rm=T)+sd(x,na.rm=T) ~ "1conservative/right",
            x < mean(x,na.rm=T)+sd(x,na.rm=T) & x > mean(x,na.rm=T)-sd(x,na.rm=T) ~ "2moderate/centre",
            x < mean(x,na.rm=T)-sd(x,na.rm=T) ~ "3liberal/left")
}


df <-
  df %>%
  dplyr::group_by(country) %>%
  dplyr::mutate(political_ideology_3groups = interaction_fun(political_ideology)
                , national_pi_mean = mean(political_ideology)
                , national_pi_sd = sd(political_ideology))

```

## Plot

Figure \@ref(fig:hygieneMIsNZLUSA1) shows the relationship between Political Ideology and Internal Moral Identity in predicting Physical Hygiene for the New Zealand sample and the USA sample separately (note that these effects are equivalent).

```{r hygieneMIsNZLUSA1, fig.cap="USA: Interaction between Political Ideology and Internal Moral Identity in predicting Physical Hygiene", include=TRUE, message=FALSE, fig.height=3}
df1 <- df[which(df$country=="USA"|df$country=="NZL"),]
g <- ggplot(df1, aes(moral_identity_internal, physical_hygiene_tot, linetype =political_ideology_3groups))+
  geom_jitter(height = .1, width = .1, size=.0001, color="gray") + 
  #ylim(0,12) +
  geom_smooth(method=lm, size = .5, color="black") +
  labs(y = "Physical Hygiene",
       x = "Internal Moral Identity",
       linetype = "Political Ideology"
       )+
  theme_apa()+
  scale_linetype_manual(values = c("longdash", "solid", "dotted"),
                    labels=c("Conservative",
                           "Moderate",
                           "Liberal"))+
  facet_wrap(df1$country)+
  theme_bw()+
  theme(plot.title=element_text(#family="Times",
                                size=12
                                )
        , legend.text=element_text(#family="Times",
                                 size=8
                                 )
        , legend.title=element_text(#family="Times",
                                    size=10
                                    )
        , axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 )
        , axis.ticks.x = element_blank()
        , axis.title=element_text(#family="Times",
                                  size=12
                                  )
        , strip.text=element_text(#family = "Times",
                                  size = 12
                                  )
        , strip.background = element_rect(fill = NA, size = 1,
                                           colour = "white"
                                          )
        , panel.border = element_blank()
        , axis.line.x = element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , axis.line.y = # element_blank()
          element_line(size = 0.1
                                     , linetype = "solid", colour = "black")
        , legend.position="right"
        , panel.spacing = unit(2, "lines")
        )

suppressWarnings(print(g))
  
```

## USA Regression

```{r}
fit1 <- lm(
  physical_hygiene_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = usa)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r usaregression3, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Adherence to Physical Hygiene measures in USA"
)

```


## New Zealand Regression

```{r}
fit1 <- lm(
  physical_hygiene_tot ~
            risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          + # add predictors
          + moral_circle
          + moral_identity_internal
          + moral_identity_symbolic
          + political_ideology
          + (moral_identity_internal*moral_circle)
          + (moral_identity_symbolic*moral_circle)
          + (moral_identity_internal*political_ideology)
          + (moral_identity_symbolic*political_ideology)
          , data = nzl)
summary(fit1)

apa_lm <- apa_print(fit1)

```

This model was significant `r apa_lm$full_result$modelfit`.

```{r nzlregression3, include=TRUE}

apa_table(
  apa_lm$table
  , caption = "Predictors of Adherence to Physical Hygiene measures in New Zealand"
)

```


