---
title: "COVID-19 Many Labs Study"
subtitle: "Pre-Registration Ideas for Irish Team"
author: "Cillian McHugh, Siobhán M. Griffin, Darragh McGashin, Paul J. Maher"
date: "15th August 2020"
bibliography: "../../Research_general/resources/bib/My Library.bib"
csl: "../../Research_general/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---
<style type="text/css">
  .table-container {
  width: 100%;
  overflow-x: scroll;
}
</style>


# First Look

In this document I have provided a brief overview of some of the relationships between the variables in the Irish sample and in 10% of the International sample. This is intended to guide the feasibility of our proposed hypotheses for pre-registration to access the full dataset. 

### Notes

- Some of the tables below are difficult to read/navigate. Apologies, it is tricky to try and include enough information to be meaningful, without presenting it in a way that is overwhelming
- I have included a Google doc at the end of this for content relating to the preregistration.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
```

```{r}

# <script>
# $(document).ready(function() {
#   $items = $('div#TOC li');
#   $items.each(function(idx) {
#     num_ul = $(this).parentsUntil('#TOC').length;
#     $(this).css({'text-indent': num_ul * 10, 'padding-left': 10});
#   });
# 
# });
# </script>

# output:
#   bookdown::html_document2:
#     fig_caption: yes
#     toc: true
#     toc_float:
#       toc_collapsed: false
#     toc_depth: 4
#     number_sections: false
# editor_options: 
#   chunk_output_type: console

```


```{r loadlibraries}
rm(list=ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
library(desnum)
library(papaja)
library(purrr)
library(interactions)
library(kableExtra)
library(data.table)
```

```{r load_data}
#setwd("../COVID_19/many_labs")
#source("set_up_data.R")
load("../many_labs/COVID_manylabs_data.RData")

```

```{r basiccorrelationsIreland}

df <- Ireland_c

cor.test(df$moral_identity_internal,df$moral_identity_symbolic)
plot(df$moral_identity_internal,df$moral_identity_symbolic)
abline(lm(df$moral_identity_internal~df$moral_identity_symbolic))

totals <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , psych_wellbeing_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , open_minded_tot
      , morality_as_cooperat_1
      , morality_as_cooperat_2
      , morality_as_cooperat_3
      , morality_as_cooperat_4
      , morality_as_cooperat_5
      , morality_as_cooperat_6
      , trait_optimism_tot
      , social_belonging_tot
      , self_control_tot
      , self_esteem
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}


totals(df) 
 
#x <- daply(df, .(Country), function(x)return(x))
#x <- df %>% group_by(country) %>%  group_split(country)


#x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )
#y <- lapply(x, totals)
y <- totals(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P

#corrplot(mydata.cor)

```

# Irish Sample Overview

Once incomplete responses had been removed we were left with a sample of *N* = `r length(df$sex)` participants (`r sum(df$sex=="Female")`, female, `r sum(df$sex=="Male")` male, *M*~age~ = `r round(mean(df$age),digits=2)`, min = `r min(df$age)`, max = `r max(df$age)`, *SD* = `r round(sd(df$age),digits=2)`) recruited primarily through snowball sampling (*n*~snowball~ = `r sum(df$survey=="snowball")`, *n*~prolific~ = `r sum(df$survey=="prolific")`). 

## Basic Correlations in Ireland

Below is a correlation table for (almost) all the variables. Direction and strength of correlation indicated by colour and relative intensity. The correlation coefficients are displayed for each relationship within Figure\ \@ref(fig:plotireland) (and relevant *p* values are displayed in Table\ \@ref(tab:corpvaluesireland)).

```{r plotireland, fig.cap="Correlation coefficients for all correlations in the Irish sample", fig.height=10, fig.width=15, out.width = '180%',, include=TRUE}

cor.plot(z, las=2, MAR = 8, cex=0.9)

```

<div class=table-container>
```{r corpvaluesireland,  include=TRUE}

ps <- round(mydata.p, digits=3)

#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , psych_wellbeing_tot       = "N/A"       
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , open_minded_tot           = "N/A"   
      , morality_as_cooperat_1    = "N/A"   
      , morality_as_cooperat_2    = "N/A"   
      , morality_as_cooperat_3    = "N/A"   
      , morality_as_cooperat_4    = "N/A"   
      , morality_as_cooperat_5    = "N/A"   
      , morality_as_cooperat_6    = "N/A"   
      , trait_optimism_tot        = "N/A"      
      , social_belonging_tot      = "N/A" 
      , self_control_tot          = "N/A"           
      , self_esteem               = "N/A"             
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                                     , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , psych_wellbeing_tot = cell_spec(psych_wellbeing_tot, "html", color = ifelse(psych_wellbeing_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , open_minded_tot = cell_spec(open_minded_tot, "html", color = ifelse(open_minded_tot <.05, "red", "black"))
  , morality_as_cooperat_1 = cell_spec(morality_as_cooperat_1, "html", color = ifelse(morality_as_cooperat_1 <.05, "red", "black"))
  , morality_as_cooperat_2 = cell_spec(morality_as_cooperat_2, "html", color = ifelse(morality_as_cooperat_2 <.05, "red", "black"))
  , morality_as_cooperat_3 = cell_spec(morality_as_cooperat_3, "html", color = ifelse(morality_as_cooperat_3 <.05, "red", "black"))
  , morality_as_cooperat_4 = cell_spec(morality_as_cooperat_4, "html", color = ifelse(morality_as_cooperat_4 <.05, "red", "black"))
  , morality_as_cooperat_5 = cell_spec(morality_as_cooperat_5, "html", color = ifelse(morality_as_cooperat_5 <.05, "red", "black"))
  , morality_as_cooperat_6 = cell_spec(morality_as_cooperat_6, "html", color = ifelse(morality_as_cooperat_6 <.05, "red", "black"))
  , trait_optimism_tot = cell_spec(trait_optimism_tot, "html", color = ifelse(trait_optimism_tot <.05, "red", "black"))
  , social_belonging_tot = cell_spec(social_belonging_tot, "html", color = ifelse(social_belonging_tot <.05, "red", "black"))
  , self_control_tot = cell_spec(self_control_tot, "html", color = ifelse(self_control_tot <.05, "red", "black"))
  , self_esteem = cell_spec(self_esteem, "html", color = ifelse(self_esteem <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 1") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:25, font_size = 9)


```
</div>

```{r basiccorrelationsworld}

df <- World_full_c

cor.test(df$moral_identity_internal,df$moral_identity_symbolic)
plot(df$moral_identity_internal,df$moral_identity_symbolic)
abline(lm(df$moral_identity_internal~df$moral_identity_symbolic))



totals(df) 
 
#x <- daply(df, .(Country), function(x)return(x))
#x <- df %>% group_by(country) %>%  group_split(country)


x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )
y <- lapply(x, totals)
ytot <- totals(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

z <- lapply(y, mydata_cor_fun)

ztot <- mydata_cor_fun(ytot)
#mydata.cor

#corrplot(z)
#cor.plot(z, las=2)
mydata.rcorr = rcorr(as.matrix(ztot))
#mydata.rcorr = rcorr(as.matrix(mydata))
#mydata.rcorr

mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


#corrplot(mydata.cor)

```

# International Sample Overview

Randomly selected 10% of the International sample resulted in a sample of *N* = `r length(df$sex)` participants (`r sum(df$sex==1, na.rm=T)`, female, `r sum(df$sex==2, na.rm=T)` male,  `r sum(df$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(df$age,na.rm=T),digits=2)`, min = `r min(df$age)`, max = `r max(df$age)`, *SD* = `r round(sd(df$age,na.rm=T),digits=2)`), from `r length(levels(df$country))` countries. Breakdown of the number of participants from each country in the sample is displayed in Table\ \@ref(tab:countrybreakdown).

<div class=table-container>
```{r countrybreakdown, include=TRUE}
`colnames<-`(as.data.frame(table(df$country)),c("Country", "N")) %>% 
  kable(format = "html", escape = F, caption = "Breakdown of total N by Country")%>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:25, font_size = 9)
```
</div>

## Basic International Correlations

As with the Irish sample, I have put together a basic correlation table for most of the variables in Figure\ \@ref(fig:plotworld), with the relevant *p* values in Table\ \@ref(tab:corpvaluesworld)).

```{r plotworld, fig.cap="Correlation coefficients for all correlations in the International sample", fig.height=10, fig.width=15, out.width = '180%', include=TRUE}

cor.plot(ztot, las=2, MAR = 8, cex=0.9)

```

<div class=table-container>
```{r corpvaluesworld, include=TRUE}

ps <- round(mydata.p, digits=3)

#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , psych_wellbeing_tot       = "N/A"       
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , open_minded_tot           = "N/A"   
      , morality_as_cooperat_1    = "N/A"   
      , morality_as_cooperat_2    = "N/A"   
      , morality_as_cooperat_3    = "N/A"   
      , morality_as_cooperat_4    = "N/A"   
      , morality_as_cooperat_5    = "N/A"   
      , morality_as_cooperat_6    = "N/A"   
      , trait_optimism_tot        = "N/A"      
      , social_belonging_tot      = "N/A" 
      , self_control_tot          = "N/A"           
      , self_esteem               = "N/A"             
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                                     , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , psych_wellbeing_tot = cell_spec(psych_wellbeing_tot, "html", color = ifelse(psych_wellbeing_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , open_minded_tot = cell_spec(open_minded_tot, "html", color = ifelse(open_minded_tot <.05, "red", "black"))
  , morality_as_cooperat_1 = cell_spec(morality_as_cooperat_1, "html", color = ifelse(morality_as_cooperat_1 <.05, "red", "black"))
  , morality_as_cooperat_2 = cell_spec(morality_as_cooperat_2, "html", color = ifelse(morality_as_cooperat_2 <.05, "red", "black"))
  , morality_as_cooperat_3 = cell_spec(morality_as_cooperat_3, "html", color = ifelse(morality_as_cooperat_3 <.05, "red", "black"))
  , morality_as_cooperat_4 = cell_spec(morality_as_cooperat_4, "html", color = ifelse(morality_as_cooperat_4 <.05, "red", "black"))
  , morality_as_cooperat_5 = cell_spec(morality_as_cooperat_5, "html", color = ifelse(morality_as_cooperat_5 <.05, "red", "black"))
  , morality_as_cooperat_6 = cell_spec(morality_as_cooperat_6, "html", color = ifelse(morality_as_cooperat_6 <.05, "red", "black"))
  , trait_optimism_tot = cell_spec(trait_optimism_tot, "html", color = ifelse(trait_optimism_tot <.05, "red", "black"))
  , social_belonging_tot = cell_spec(social_belonging_tot, "html", color = ifelse(social_belonging_tot <.05, "red", "black"))
  , self_control_tot = cell_spec(self_control_tot, "html", color = ifelse(self_control_tot <.05, "red", "black"))
  , self_esteem = cell_spec(self_esteem, "html", color = ifelse(self_esteem <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 2") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:25, font_size = 9)


```
</div>

## Correlations by Country

```{r plotworldbycountry, include=FALSE}
#levels(df$country)
# table(df$country)
# 
# loop_sort <- function(ppn){
#   corrplot(z[[ppn]], title = paste(names(z[ppn])))
#   
#   }
# 
# lapply(1:14, loop_sort)
#  
# lapply(16:66, loop_sort)


```


```{r, include=FALSE}
# levels(df$country)
# table(df$country)
# 
# loop_sort <- function(ppn){
#   corrplot(z[[ppn]], title = paste(names(z[ppn])))
#   
#   }
# lapply(1:14, loop_sort)
#  
# lapply(16:66, loop_sort)


```


```{r, graphsbycountry, include=TRUE}

# tapply(df$moral_identity_symbolic, df$Country, descriptives)
# 
# 
# moral_id_S_anova <- 
#   aov_car(
#     moral_identity_symbolic ~ Country + Error(X1)
#     , data = df
#     , type = 3
#     
#   )
# 
# moral_id_S_anova_results <- apa_print(moral_id_S_anova, es = "pes")
# moral_id_S_anova_results
# 
# 
# loop_sort(1)
# [1]
# loop_sort(2)
# loop_sort(3)
# loop_sort(4)
# loop_sort(5)
# loop_sort(6)
# loop_sort(7)
# loop_sort(8)
# loop_sort(9)
# loop_sort(10)
# loop_sort(11)
# loop_sort(12)
# loop_sort(13)
# loop_sort(14)
# loop_sort(15)
# loop_sort(16)
# loop_sort(17)
# loop_sort(18)
# loop_sort(19)
# loop_sort(20)
# loop_sort(21)
# loop_sort(22)
# loop_sort(23)
# loop_sort(24)
# loop_sort(25)
# loop_sort(26)
# loop_sort(27)
# loop_sort(28)
# loop_sort(29)
# loop_sort(30)
# loop_sort(31)
# loop_sort(32)
# loop_sort(33)
# loop_sort(34)
# loop_sort(35)
# loop_sort(36)
# loop_sort(37)
# loop_sort(38)
# loop_sort(39)
# loop_sort(40)
# loop_sort(41)
# loop_sort(42)
# loop_sort(43)
# loop_sort(44)
# loop_sort(45)
# loop_sort(46)
# loop_sort(47)
# loop_sort(48)
# loop_sort(49)
# loop_sort(50)
# loop_sort(51)
# loop_sort(52)
# loop_sort(53)
# loop_sort(54)
# loop_sort(55)
# loop_sort(56)
# loop_sort(57)
# loop_sort(58)
# loop_sort(59)
# loop_sort(60)
# loop_sort(61)
# loop_sort(62)
# loop_sort(63)
# loop_sort(64)
# loop_sort(65)
# loop_sort(66)
```


# Some Expected Relationships

Below I have identified specific variables of interest, and some variables that (I think) should be controlled for. I'm primarily interested in the combined influence of **moral identity** and **moral circle** (and/or **political identity**) on **adherence to relevant measures**, and **policy support**. I have included a suite of variables that might be worth controlling for (or trying to control for); these are: *collective narcissism*, *national identification*, *conspiracy beliefs*, *narcissism*, and *risk perception*.

Given that my hypotheses are derived primarily from the discourse in the US, I have provided three versions of the following correlations. First I provide the relationships in the Irish context, then on US sample, and finally the International sample

```{r}
variables_of_interest <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}
```
## Basic Correlations 
### Ireland

```{r}

df <- Ireland_c


y <- variables_of_interest(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


```


```{r plotinterest, fig.cap="Correlation coefficients for relevant correlations in the Irish sample", fig.height=10, fig.width=15, out.width = '180%',, include=TRUE}

cor.plot(z, las=2, MAR = 8, cex=0.9)

```

<div class=table-container>
```{r corpvaluesinterest,  include=TRUE}

ps <- round(mydata.p, digits=3)
#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                    , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 3") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:13, font_size = 9)


```
</div>

### USA

```{r}
USA <- World_full_c[which(World_full_c$country=="USA"),]
#df <- World_part_c[which(World_part_c$country=="USA"),]
df <- USA

y <- variables_of_interest(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


```

```{r plotinterestUS, fig.cap="Correlation coefficients for relevant correlations in the Irish sample", fig.height=10, fig.width=15, out.width = '180%',, include=TRUE}

cor.plot(z, las=2, MAR = 8, cex=0.9)

```

<div class=table-container>
```{r corpvaluesinterestUS,  include=TRUE}

ps <- round(mydata.p, digits=3)
#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                    , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 4") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:13, font_size = 9)


```
</div>


### World



```{r}

df <- World_full_c


y <- variables_of_interest(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


```




```{r plotinterestworld, fig.cap="Correlation coefficients for relevant correlations in the Irish sample", fig.height=10, fig.width=15, out.width = '180%',, include=TRUE}

cor.plot(z, las=2, MAR = 8, cex=0.9)

```

<div class=table-container>
```{r corpvaluesinterestworld,  include=TRUE}

ps <- round(mydata.p, digits=3)
#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                    , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 5") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:13, font_size = 9)


```
</div>


## Basic Regressions

### Ireland
#### Policy Support

```{r include = TRUE, size="tiny"}

options(width = 1000)
df <- Ireland_c

message("Predictors of Policy Support")

fit <- lm(policy_support_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)
summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of Policy Support.")
```

#### Physical Contact Measures

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Contact measures")

fit <- lm(physical_contact_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Contact measures.")
```

#### Physical Hygiene measures 

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Hygiene measures")

fit <- lm(physical_hygiene_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Hygiene measures.")
```



### USA
#### Policy Support
```{r include = TRUE, size="tiny"}
options(width = 1000)
#USA <- World_part_c[which(World_part_c$country=="USA"),]
df <- USA
message("Predictors of Policy Support")

fit <- lm(policy_support_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of Policy Support.")
```

#### Physical Contact Measures

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Contact measures")

fit <- lm(physical_contact_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Contact measures.")
```

#### Physical Hygiene measures

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Hygiene measures")

fit <- lm(physical_hygiene_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Hygiene measures.")
```




### World
#### Policy Support
```{r include = TRUE, size="tiny"}

options(width = 1000)
df <- World_full_c

message("Predictors of Policy Support")

fit <- lm(policy_support_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of Policy Support.")
```

#### Physical Contact Measures

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Contact measures")

fit <- lm(physical_contact_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Contact measures.")
```

#### Physical Hygiene measures

```{r include = TRUE, size="tiny"}
message("Predictors of adherence to Physical Hygiene measures")

fit <- lm(physical_hygiene_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot + conspiracy_tot + national_ID_tot, df)

summary(fit)
apa_lm <- apa_print(fit)
```

```{r include=TRUE, results='asis'}

apa_table(apa_lm$table
          , caption = "Predictors of adherence to Physical Hygiene measures.")
```



## Some Basic Interaction Plots

Below I have plotted the interactions that emerged significant in the regressions above to help visualise the relationships.

- On the Political ideology dimension, higher scores are more conservative, and lower scores are more liberal.
- Higher scores for Moral Circle indicate a larger moral circle.

### Ireland

```{r irishinteractionplots, include=TRUE}
df <- Ireland_c

message("Interaction between Symbolic Moral Identity and Moral Circle in predicting Policy support")
fit <- lm(policy_support_tot ~ moral_identity_symbolic*moral_circle , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = moral_circle)

message("Interaction between Symbolic Moral Identity and Moral Circle in predicting adherence to Physical Contact measures")
fit <- lm(physical_contact_tot ~ moral_identity_symbolic*moral_circle , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = moral_circle)

message("No significant interactions relating to Physical Hygiene")

```

### USA

```{r USAinteractionplots, include=TRUE}
df <- USA

message("Interaction between Symbolic Moral Identity and Political Ideology in predicting Policy support")
fit <- lm(policy_support_tot ~ moral_identity_symbolic*political_ideology , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = political_ideology)

message("No significant interactions relating to Physical Contact measures")


message("No significant interactions relating to Physical Hygiene measures")

```

### World

```{r worldinteractionplots, include=TRUE}
df <- World_full_c

message("Interaction between Symbolic Moral Identity and Political Ideology in predicting Policy support")
fit <- lm(policy_support_tot ~ moral_identity_symbolic*political_ideology , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = political_ideology)

message("Interaction between Symbolic Moral Identity and Moral Circle in predicting adherence to Physical Contact measures")
fit <- lm(physical_contact_tot ~ moral_identity_symbolic*moral_circle , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = moral_circle)

message("Interaction between Symbolic Moral Identity and Moral Circle in predicting adherence to Physical Hygiene measures")
fit <- lm(physical_hygiene_tot ~ moral_identity_symbolic*political_ideology , df)
summary(fit)
interact_plot(model = fit, pred = moral_identity_symbolic, modx = political_ideology)
```

```{r baciccorsinterest}

df <- World_full_c

cor.test(df$moral_identity_internal,df$moral_identity_symbolic)
plot(df$moral_identity_internal,df$moral_identity_symbolic)
abline(lm(df$moral_identity_internal~df$moral_identity_symbolic))



totals(df) 
 
#x <- daply(df, .(Country), function(x)return(x))
#x <- df %>% group_by(country) %>%  group_split(country)


x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )
y <- lapply(x, totals)
ytot <- totals(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

z <- lapply(y, mydata_cor_fun)

ztot <- mydata_cor_fun(ytot)
#mydata.cor

#corrplot(z)
#cor.plot(z, las=2)
mydata.rcorr = rcorr(as.matrix(ztot))
#mydata.rcorr = rcorr(as.matrix(mydata))
#mydata.rcorr

mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


#corrplot(mydata.cor)

```


```{r}

df <- Ireland_c



df <- Ireland_c

df <- World_full_c[which(World_full_c$country=="USA"),]

df <- World_full_c


fit <- lm(policy_support_tot ~ (moral_identity_internal + moral_identity_symbolic)*(moral_circle+political_ideology) + risk_perception_tot + narcissism_admiration_tot + narcissism_rivalry_tot + collective_narcissism_tot , df)




fit <- lm(policy_support_tot ~ moral_identity_symbolic*political_ideology , df)
summary(fit)

interact_plot(model = fit, pred = moral_identity_symbolic, modx = political_ideology)


```

# Checking Policy interaction for all countries

```{r, include=TRUE}
x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )

lm_fun <- function(x){
  lm(policy_support_tot
          ~ risk_perception_tot
          + narcissism_admiration_tot
          + narcissism_rivalry_tot
          + collective_narcissism_tot
          + conspiracy_tot
          + national_ID_tot
          ### add predictors
          + moral_identity_internal
          + moral_identity_symbolic
          + moral_circle
          + political_ideology
          ### add interactions
          + (moral_identity_internal + moral_identity_symbolic) : (moral_circle+political_ideology)
          , data = x
     )
}


all_lms <- lapply(x, lm_fun)
summary_lms <- lapply(all_lms, summary)
summary_lms

#### testing something else ####

sig_interactions <- function(x){
  test <- x$coefficients["moral_identity_internal:moral_circle",]
  test
}
loop_ps <- function(){lapply(summary_lms, sig_interactions)}
sig_interactions <- do.call(rbind, loop_ps())
sig_interactions <- as.data.frame(sig_interactions)
moralIDi_MoralCircle <- sig_interactions[which(sig_interactions$`Pr(>|t|)`<.05),]

sig_interactions <- function(x){
  test <- x$coefficients["moral_identity_internal:political_ideology",]
  test
}
loop_ps <- function(){lapply(summary_lms, sig_interactions)}
sig_interactions <- do.call(rbind, loop_ps())
sig_interactions <- as.data.frame(sig_interactions)
moralIDi_PI <- sig_interactions[which(sig_interactions$`Pr(>|t|)`<.05),]

sig_interactions <- function(x){
  test <- x$coefficients["moral_identity_symbolic:moral_circle",]
  test
}
loop_ps <- function(){lapply(summary_lms, sig_interactions)}
sig_interactions <- do.call(rbind, loop_ps())
sig_interactions <- as.data.frame(sig_interactions)
moralIDs_MoralCircle <- sig_interactions[which(sig_interactions$`Pr(>|t|)`<.05),]

sig_interactions <- function(x){
  test <- x$coefficients["moral_identity_symbolic:political_ideology",]
  test
}
loop_ps <- function(){lapply(summary_lms, sig_interactions)}
sig_interactions <- do.call(rbind, loop_ps())
sig_interactions <- as.data.frame(sig_interactions)
moralIDs_PI <- sig_interactions[which(sig_interactions$`Pr(>|t|)`<.05),]

moralIDi_MoralCircle
moralIDi_PI
moralIDs_MoralCircle
moralIDs_PI



### moral_identity_internal:moral_circle ###
ps_MIiMC <- function(x){
  test <- x$coefficients["moral_identity_internal:moral_circle",]
  test["Pr(>|t|)"]
}
MIiMC <- lapply(summary_lms, ps_MIiMC)
which(MIiMC<.05)

### moral_identity_internal:political_ideology ###
ps_MIiPI <- function(x){
  test <- x$coefficients["moral_identity_internal:political_ideology",]
  test["Pr(>|t|)"]
}
MIiPI <- lapply(summary_lms, ps_MIiPI)
which(MIiPI<.05)

### moral_identity_symbolic:moral_circle ###
ps_MIsMC <- function(x){
  test <- x$coefficients["moral_identity_symbolic:moral_circle",]
  test["Pr(>|t|)"]
}
MIsMC <- lapply(summary_lms, ps_MIsMC)
which(MIsMC<.05)

### moral_identity_symbolic:political_ideology ###
ps_MIsPI <- function(x){
  test <- x$coefficients["moral_identity_symbolic:political_ideology",]
  test["Pr(>|t|)"]
}
MIsPI <- lapply(summary_lms, ps_MIsPI)
MIsPI[which(MIsPI<.05)]






```


# Shared Document for Preregistration

<iframe width="860" height="1100" src="https://docs.google.com/document/d/1t6oN5rrMxRupFUkY7cTlgaJ0dDBZN34w6WnVVgTuH0w/edit?rm=minimal" frameborder="0"></iframe>

 <a href="https://docs.google.com/document/d/1t6oN5rrMxRupFUkY7cTlgaJ0dDBZN34w6WnVVgTuH0w/edit?usp=sharing" target="_blank">click here to edit in separate window</a> 


