---
title: "COVID-19, Morality, and Political Ideology"
subtitle: "Supplementary Information"
author: "Cillian McHugh"
date: "6th October 2020"
bibliography: "../../Research_general/resources/bib/My Library.bib"
csl: "../../Research_general/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---
<style type="text/css">
  .table-container {
  width: 100%;
  overflow-x: scroll;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)

# https://www.finex.co/how-to-display-html-in-github/
# https://cillianmiltown.github.io/many_labs_covid19/third_look_ideas.html
```

```{r loadlibraries}
rm(list=ls())
library(tidyverse)
library(plyr)
library(psych)
library(skimr)
library(corrplot)
library(Hmisc)
#library(psy)
library(afex)
library(desnum)
library(papaja)
library(purrr)
library(interactions)
library(kableExtra)
library(data.table)
```

```{r load_data}
#setwd("../COVID_19/many_labs")
#source("set_up_data.R")
load("../many_labs/COVID_manylabs_data.RData")

df <- World_full_c
```


# Sample Overview

A total of *N* = `r length(df$sex)` participants (`r sum(df$sex==1, na.rm=T)`, female, `r sum(df$sex==2, na.rm=T)` male,  `r sum(df$sex==3, na.rm=T)` other, *M*~age~ = `r round(mean(df$age,na.rm=T),digits=2)`, min = 18, max = 100, *SD* = `r round(sd(df$age,na.rm=T),digits=2)`), from `r length(levels(df$country))` countries took part in the study. Breakdown of the number of participants from each country in the sample is displayed in Table\ \@ref(tab:countrybreakdown).

<div class=table-container>
```{r countrybreakdown, include=TRUE}
`colnames<-`(`rownames<-`(
  as.data.frame(t(
    as.data.frame(table(df$country))
  ))
  ,c("Country", "N")),NULL)%>% 
  kable(format = "html", escape = F, caption = "Breakdown of total N by Country")%>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(1:2, font_size = 9)
```
</div>



# Basic Correlations (Full Sample)


```{r}
variables_of_interest <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}
```

```{r}

df <- World_full_c


y <- variables_of_interest(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P


```


## Coefficients

```{r plotinterestworld, fig.cap="Correlation coefficients for relevant correlations in the Irish sample", fig.height=10, fig.width=15, out.width = '180%',, include=TRUE}

cor.plot(z, las=2, MAR = 8, cex=0.9)

```

## p-values

<div class=table-container>
```{r corpvaluesinterestworld,  include=TRUE}

ps <- round(mydata.p, digits=3)
#ps <- as.data.frame(mydata.p)

ps <- as.data.frame(ps)

ps %>% replace_na(list(
        physical_contact_tot      = "N/A" 
      , physical_hygiene_tot      = "N/A"  
      , policy_support_tot        = "N/A"      
      , collective_narcissism_tot = "N/A"             
      , national_ID_tot           = "N/A"   
      , conspiracy_tot            = "N/A"         
      , narcissism_admiration_tot = "N/A"      
      , narcissism_rivalry_tot    = "N/A"   
      , moral_identity_internal   = "N/A"    
      , moral_identity_symbolic   = "N/A"    
      , risk_perception_tot       = "N/A"       
      , political_ideology        = "N/A" 
      , moral_circle              = "N/A"    )) %>% 
  mutate(
    physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
  , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                    , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
  , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
  , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
  , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
  , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
  , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
  , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
  , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
  , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
  , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
  , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
                                                                                )%>%
  kable(format = "html", escape = F, caption = "All p values for correlations displayed in Figure 5") %>%
  kable_styling("striped", full_width = F) %>% 
  row_spec(0:13, font_size = 9)


```
</div>


# Correlations by Country

## Coefficients (by Country)

Please note that generating these correlation tables resulted in duplicate unformatted output being attached to the bottom. Apologies for this, use the navigator on the left to avoid having to scroll through this.

```{r}
variables_of_interest <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}


totals <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , psych_wellbeing_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , open_minded_tot
      , morality_as_cooperat_1
      , morality_as_cooperat_2
      , morality_as_cooperat_3
      , morality_as_cooperat_4
      , morality_as_cooperat_5
      , morality_as_cooperat_6
      , trait_optimism_tot
      , social_belonging_tot
      , self_control_tot
      , self_esteem
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}

```


```{r plotworldbycountry, include=FALSE}

variables_of_interest <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}

x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )
y <- lapply(x, totals)
y <- lapply(y, variables_of_interest)

mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- lapply(y, mydata_cor_fun)

# z <- lapply(y, variables_of_interest)
#z <- na.omit(z)
levels(df$country)
table(df$country)

loop_sort <- function(ppn){
  cor.plot(z[[ppn]], main = paste(names(z[ppn])))

  }

#loop_sort(9)



#corrplot(z[[1]], title = paste(names(z[1])))

#cor.plot(z[[1]], main = paste(names(z[1])))



#### for ps #####

#do.call(rcorr, lapply(y, as.matrix))
#lapply(y, rcorr)
#mydata.rcorr = rcorr(as.matrix(y))

loop_sort_table <- function(ppn){
  mydata.rcorr <- rcorr(as.matrix(y[[ppn]]))
  mydata.p <- mydata.rcorr$P
  ps <- round(mydata.p, digits=3)
  ps <- as.data.frame(ps)
  
  p_table <- ps %>% replace_na(list(
    physical_contact_tot      = "N/A" 
    , physical_hygiene_tot      = "N/A"  
    , policy_support_tot        = "N/A"      
    , collective_narcissism_tot = "N/A"             
    , national_ID_tot           = "N/A"   
    , conspiracy_tot            = "N/A"         
    , narcissism_admiration_tot = "N/A"      
    , narcissism_rivalry_tot    = "N/A"   
    , moral_identity_internal   = "N/A"    
    , moral_identity_symbolic   = "N/A"    
    , risk_perception_tot       = "N/A"       
    , political_ideology        = "N/A" 
    , moral_circle              = "N/A"    )) %>% 
    mutate(
      physical_contact_tot = cell_spec(physical_contact_tot, "html", color = ifelse(physical_contact_tot <.05, "red", "black"))
      , physical_hygiene_tot = cell_spec(physical_hygiene_tot, "html", color = ifelse(physical_hygiene_tot <.05, "red", "black"))                    , policy_support_tot = cell_spec(policy_support_tot, "html", color = ifelse(policy_support_tot <.05, "red", "black"))
      , collective_narcissism_tot = cell_spec(collective_narcissism_tot, "html", color = ifelse(collective_narcissism_tot <.05, "red", "black"))
      , national_ID_tot = cell_spec(national_ID_tot, "html", color = ifelse(national_ID_tot <.05, "red", "black"))
      , conspiracy_tot = cell_spec(conspiracy_tot, "html", color = ifelse(conspiracy_tot <.05, "red", "black"))
      , narcissism_admiration_tot = cell_spec(narcissism_admiration_tot, "html", color = ifelse(narcissism_admiration_tot <.05, "red", "black"))
      , narcissism_rivalry_tot = cell_spec(narcissism_rivalry_tot, "html", color = ifelse(narcissism_rivalry_tot <.05, "red", "black"))
      , moral_identity_internal = cell_spec(moral_identity_internal, "html", color = ifelse(moral_identity_internal <.05, "red", "black"))
      , moral_identity_symbolic = cell_spec(moral_identity_symbolic, "html", color = ifelse(moral_identity_symbolic <.05, "red", "black"))
      , risk_perception_tot = cell_spec(risk_perception_tot, "html", color = ifelse(risk_perception_tot <.05, "red", "black"))
      , political_ideology = cell_spec(political_ideology, "html", color = ifelse(political_ideology <.05, "red", "black"))
      , moral_circle = cell_spec(moral_circle, "html", color = ifelse(moral_circle <.05, "red", "black"))
    )%>%
    kable(format = "html", escape = F, caption = paste(names(y[ppn]))) %>%
    kable_styling("striped", full_width = F) %>% 
    row_spec(0:13, font_size = 9)
  noquote(paste("<div class=table-container>",p_table,"</div>"))
}

```

```{r, include = TRUE}
lapply(1:67, loop_sort)
```

## p-values (by Country)

Please note that generating these correlation tables resulted in duplicate unformatted output being attached to the bottom. Apologies for this, use the navigator on the left to avoid having to scroll through this.

```{r, include=TRUE, results='asis'}
# 
# p_table <- loop_sort_table(2)
# 
# print(paste("<div class=table-container>","</div>"))
# 
# noquote(paste("<div class=table-container>","</div>"))
# 
# 
# help("paste")
# loop_sort_table(2)


lapply(1:67, loop_sort_table)

```


```{r, graphsbycountry, include=TRUE}

# tapply(df$moral_identity_symbolic, df$Country, descriptives)
# 
# 
# moral_id_S_anova <- 
#   aov_car(
#     moral_identity_symbolic ~ Country + Error(X1)
#     , data = df
#     , type = 3
#     
#   )
# 
# moral_id_S_anova_results <- apa_print(moral_id_S_anova, es = "pes")
# moral_id_S_anova_results
# 
# 
# loop_sort(1)
# [1]
# loop_sort(2)
# loop_sort(3)
# loop_sort(4)
# loop_sort(5)
# loop_sort(6)
# loop_sort(7)
# loop_sort(8)
# loop_sort(9)
# loop_sort(10)
# loop_sort(11)
# loop_sort(12)
# loop_sort(13)
# loop_sort(14)
# loop_sort(15)
# loop_sort(16)
# loop_sort(17)
# loop_sort(18)
# loop_sort(19)
# loop_sort(20)
# loop_sort(21)
# loop_sort(22)
# loop_sort(23)
# loop_sort(24)
# loop_sort(25)
# loop_sort(26)
# loop_sort(27)
# loop_sort(28)
# loop_sort(29)
# loop_sort(30)
# loop_sort(31)
# loop_sort(32)
# loop_sort(33)
# loop_sort(34)
# loop_sort(35)
# loop_sort(36)
# loop_sort(37)
# loop_sort(38)
# loop_sort(39)
# loop_sort(40)
# loop_sort(41)
# loop_sort(42)
# loop_sort(43)
# loop_sort(44)
# loop_sort(45)
# loop_sort(46)
# loop_sort(47)
# loop_sort(48)
# loop_sort(49)
# loop_sort(50)
# loop_sort(51)
# loop_sort(52)
# loop_sort(53)
# loop_sort(54)
# loop_sort(55)
# loop_sort(56)
# loop_sort(57)
# loop_sort(58)
# loop_sort(59)
# loop_sort(60)
# loop_sort(61)
# loop_sort(62)
# loop_sort(63)
# loop_sort(64)
# loop_sort(65)
# loop_sort(66)
```


# Shared Notes

<iframe width="860" height="950" src="https://docs.google.com/document/d/1oljGPBogHTWcOw5ayzDSMVXgxKLAUy5HWJsECqStEyg/edit?rm=minimal" frameborder="0"></iframe>

 <a href="https://docs.google.com/document/d/1oljGPBogHTWcOw5ayzDSMVXgxKLAUy5HWJsECqStEyg/edit?usp=sharing" target="_blank">click here to edit in separate window</a> 


# Previously Shared

This section contains the files previously shared:

## Paper Draft

<iframe width="860" height="950" src="https://drive.google.com/file/d/11niZzKCE7QyIv7HAbXeezssUgqE0yeSE/preview" frameborder="0"></iframe>


## Plots

### Policy Support
#### Policy Support: Internal Moral Identity and Political Ideology

<iframe width="865" height="545" src="https://drive.google.com/file/d/1yS7o0hk_1LONIRjQfBVOVopCb1fx4EuB/preview" frameborder="0"></iframe>

#### Policy Support: Symbolic Moral Identity and Political Ideology

<iframe width="865" height="545" src="https://drive.google.com/file/d/1E4HOmGCzt_i1ylUCp1eu3eFZ5sA00sqj/preview" frameborder="0"></iframe>

### Physical Contact
#### Physical Contact: Symbolic Moral Identity and Political Ideology

<iframe width="865" height="545" src="https://drive.google.com/file/d/1z2YymyvquFW2S-APbDidNKzHs9edPFfA/preview" frameborder="0"></iframe>

### Physical Hygiene
#### Physical Hygiene: Internal Moral Identity and Political Ideology

<iframe width="865" height="545" src="https://drive.google.com/file/d/17ceCWqO9a2KzWDup05qg0UN-rTFKivEa/preview" frameborder="0"></iframe>

#### Physical Hygiene: Symbolic Moral Identity and Political Ideology

<iframe width="865" height="545" src="https://drive.google.com/file/d/1TfMXC3O-9GCeeKTBRs7iSB1JDNV9o1ug/preview" frameborder="0"></iframe>

#### Physical Hygiene: Internal Moral Identity and Moral Circle

<iframe width="865" height="545" src="https://drive.google.com/file/d/1kpUMKArznJD40MW8AUzyghwUgbKlnkIn/preview" frameborder="0"></iframe>

#### Physical Hygiene: Symbolic Moral Identity and Moral Circle

<iframe width="865" height="545" src="https://drive.google.com/file/d/1SlEjpF3Z-AptNxObSbEZrjG5ithUR5Pz/preview" frameborder="0"></iframe>



## Pre-registration document (possibly old)

<iframe width="860" height="950" src="https://docs.google.com/document/d/1t6oN5rrMxRupFUkY7cTlgaJ0dDBZN34w6WnVVgTuH0w/edit?rm=minimal" frameborder="0"></iframe>

 <a href="https://docs.google.com/document/d/1t6oN5rrMxRupFUkY7cTlgaJ0dDBZN34w6WnVVgTuH0w/edit?usp=sharing" target="_blank">click here to edit in separate window</a> 




```{r}

# <script>
# $(document).ready(function() {
#   $items = $('div#TOC li');
#   $items.each(function(idx) {
#     num_ul = $(this).parentsUntil('#TOC').length;
#     $(this).css({'text-indent': num_ul * 10, 'padding-left': 10});
#   });
# 
# });
# </script>

# output:
#   bookdown::html_document2:
#     fig_caption: yes
#     toc: true
#     toc_float:
#       toc_collapsed: false
#     toc_depth: 4
#     number_sections: false
# editor_options: 
#   chunk_output_type: console

```



```{r basiccorrelationsIreland}

df <- Ireland_c

cor.test(df$moral_identity_internal,df$moral_identity_symbolic)
plot(df$moral_identity_internal,df$moral_identity_symbolic)
abline(lm(df$moral_identity_internal~df$moral_identity_symbolic))

totals <- function(df){
  subset(df,select=c(
      physical_contact_tot
      , physical_hygiene_tot
      , policy_support_tot
      , psych_wellbeing_tot
      , collective_narcissism_tot
      , national_ID_tot
      , conspiracy_tot
      , open_minded_tot
      , morality_as_cooperat_1
      , morality_as_cooperat_2
      , morality_as_cooperat_3
      , morality_as_cooperat_4
      , morality_as_cooperat_5
      , morality_as_cooperat_6
      , trait_optimism_tot
      , social_belonging_tot
      , self_control_tot
      , self_esteem
      , narcissism_admiration_tot
      , narcissism_rivalry_tot
      , moral_identity_internal
      , moral_identity_symbolic
      , risk_perception_tot
      , political_ideology
      , moral_circle
              ))
}


totals(df) 
 
#x <- daply(df, .(Country), function(x)return(x))
#x <- df %>% group_by(country) %>%  group_split(country)


#x <- df %>% group_by(country) %>% do(data = (.)) %>% with( set_names(data, country) )
#y <- lapply(x, totals)
y <- totals(df)
#daply()

#mydata <- df %>% group_by(Country) %>% do(totals(.))


mydata_cor_fun <- function(mydata){cor(mydata, method = c("pearson"), use = "complete.obs")}

#z <- lapply(y, mydata_cor_fun)

z <- mydata_cor_fun(y)
#mydata.cor

#corrplot(z)

mydata.rcorr = rcorr(as.matrix(y))
mydata.rcorr
# 
mydata.coeff = mydata.rcorr$r
mydata.p = mydata.rcorr$P

#corrplot(mydata.cor)

```


